\plaintitle

### 2016-05-20 cscw/papers/2017/labor/trackingWork.tex
making tasks discrete, giving all of the same type to a single worker makes them faster (according to lasecki et al). todo: expand on that finding!

\subsection{Distributing Work}
In both the historical and contemporary cases,
distributed, speculative work
% seemed a reasonable way
has promised
to diffuse the costs of capital--intensive resources
(whether they were sewing machines or laboratory equipment).

@@

The insight here seems to have been that
a substantial amount of work does not necessarily need to be done in collocated space,
but can be done from one's own home or other space arranged by the worker.
Moreover, by shifting the workplace into the worker's domain,
the cost of capital involved in that work can more easily be placed on workers' backs.
While yellow--cab organizations often manage drivers in similar ways to platforms such as Uber and Lyft
(inasmuch as drivers are often considered contractors, or otherwise exempt from the formal status of ``employee''),
these new systems go further,
by framing ownership and responsibility for costs
(e.g. automotive maintenance)
on drivers.
In our fieldwork, we discovered many longtime ``on--demand'' drivers
(affiliated with platforms such as Uber and Lyft)
who readily voiced frustration with the costs of
frequent oil changes and the unexpected replacement of expensive parts.

Distributing labor had similar effects on pieceworkers at the turn of the \nth{20} century;
textile workers were given the source material with which to work,
but were generally expected to use their own sewing materials and work in their own homes
\cite{hapke2004sweatshop}.

@@

This approach paralleled what would be known as ``Taylorism'',
and its influences can be seen today in crowd work and micro--tasks.
\textit{talk about breaking tasks down both in general (Cheng) and even for the self (Teevan);
horizontal cuts instead of vertical}
\cite{cheng2015break,writingMicroTasks}.
% and might generally be regarded collectively as ``scientific management''
% The compelling solution that emerged in piecework became what we now know as Taylorism;
% rather than

>>>>

\subsection{Distributing Work}
In both the historical and contemporary cases,
distributed, speculative work
has promised
to diffuse the costs of capital--intensive resources
(whether they were sewing machines or laboratory equipment).

@@

The insight here seems to have been that
a substantial amount of work does not necessarily need to be done in collocated space,
but can be done from one's own home or other space arranged by the worker.
Moreover, by shifting the workplace into the worker's domain,
the cost of capital involved in that work can more easily be placed on workers' backs.
While yellow--cab organizations often manage drivers in similar ways to platforms such as Uber and Lyft
(inasmuch as drivers are often considered contractors, or otherwise exempt from the formal status of ``employee''),
these new systems go further,
by framing ownership and responsibility for costs
(e.g. automotive maintenance)
on drivers.
In our fieldwork, we discovered many longtime ``on--demand'' drivers
(affiliated with platforms such as Uber and Lyft)
who readily voiced frustration with the costs of
frequent oil changes and the unexpected replacement of expensive parts.
Distributing labor had similar effects on pieceworkers at the turn of the \nth{20} century;
textile workers were given the source material with which to work,
but were generally expected to use their own sewing materials and work in their own homes
\cite{hapke2004sweatshop}.

@@

This approach paralleled what would be known as ``Taylorism'',
and its influences can be seen today in crowd work and micro--tasks.
\textit{talk about breaking tasks down both in general (Cheng) and even for the self (Teevan);
horizontal cuts instead of vertical}
\cite{cheng2015break,writingMicroTasks}.
By breaking tasks into their constituent parts,
and especially as the nature of the work could be aligned with other, similar tasks,
workers could become ``experts'' in a small aspect of the work that they did,
speeding their work dramatically
\cite{delayAndOrderLasecki}.

Taylorism enabled
--- and would later become synonymous with --- 
scientific management, which we will discuss later
% and might generally be regarded collectively as ``scientific management''
% The compelling solution that emerged in piecework became what we now know as Taylorism;
% rather than
